---
title: "Documentation for the Czech Science Foundation dataset"
author: "Radim Hladik"
output: html_document
---

```{r data_csf_documentation_setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      root.dir = '/docs')
library(targets)
library(dplyr)
library(tibble)

tar_load(data_csf)

```

Observations: `r nrow(data_csf)`

Variables: `r ncol(data_csf)`

```{r head_view, echo=FALSE}

data_csf %>%
    slice_head(n =5) %>% 
    mutate(across(is.character, ~stringr::str_replace(.x,
                                                      "(^.{20}).*",
                                                      "\\1 \\.\\.\\."
                                                      ))) %>% 
    knitr::kable() 

```


## Variables - description

-   `project_code` unique identifier of a project

-   `title_cz` title of the project in Czech

-   `title_eng` title of the project in English

-   `provider` Identifier of the funding provider

    -   **GA0** Czech Science Foundation

-   `program_code` identifier of the competition program

    -   **GA** Standard projects. 1993-ongoing

    -   **GE** Eurocores

    -   **GP** Postdoctoral projects. 1998-ongoing

    -   **GC** International projects. 2007-ongoing

    -   **GD** Doctoral projects. 2003-ongoing

    -   **GB** Excellence support projects. 2012-2018

    -   **GF** LEAD Agency international projects. 2015-ongoing

    -   **GJ** Junior projects. **2015-ongoing**

    -   **GX** Excellence projects. 2019-ongoimng

-   `program_title` name of the competition program (in Czech)

-   `disc_group` field of research according to original Czech classification system (until 2017)

-   `disc` primary research discipline according to original Czech classification system (until 2017)

-   `disc_secondary` secondary research discipline according to original Czech classification system (until 2017), if multidisciplinary

-   `disc_tertiary` tertiary research discipline according to original Czech classification system (until 2017), if multidisciplinary

-   `ford` field of research according to FORD (after 2017)

-   `ford_secondary` field of research according to FORD (after 2017), if multidisciplinary

-   `ford_tertiary` field of research according to FORD (after 2017), if multidisciplinary

-   `year_start` first year of the project

-   `year_end` final year of the project

-   `research_category` classification of the type of research

    -   **ZV** basic (fundamental) research

-   `evaluation` evaluation of completed projects

    -   **V** excellent

    -   **U** - successful

    -   **O** -unsuccessful, no contract breach

    -   **S** - unsuccessful, contract breach

    -   **NA** - missing

-   `total` total amount of funding

-   `national_public` amount of funding from national public resources

-   `foreign_public` amount of funding from foreign resources

-   `private_total` amount of funding from the private sector

-   `other_public` amount of funding from other public resources

-   `abstract` description of the project goals

-   `keywords` keywords of the project
