---
title: "Documentation for the Czech Science Foundation and L'Agence Nationale de la Recherche datasets"
author: "Marc Bertin, Chérifa Boukacem-Zeghmouri, Radim Hladik "
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r data_csf_documentation_setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      knitr::opts_knit$set(root.dir = '../'))
library(targets)
library(dplyr)
library(tibble)

tar_load(data_csf)
tar_load(data_anr)
```

## Dimensions

```{r dimensions, echo=FALSE}

tibble::tibble(data = c("csf", "anr"),
               n_rows = c(nrow(data_csf), nrow(data_anr)),
               n_cols = c(ncol(data_csf), ncol(data_anr)),
               projects = c(length(unique(data_csf$project_code)),
                            length(unique(data_anr$code_du_projet))),
               min_year = c(min(as.integer(data_csf$year_start), na.rm = TRUE),
                            min(as.integer(data_anr$date_de_debut), na.rm = TRUE)),
               max_year = c(max(as.integer(data_csf$year_start), na.rm = TRUE),
                            max(as.integer(data_anr$date_de_debut), na.rm = TRUE))
               ) %>% 
    knitr::kable()

```

## Summaries

### CSF data

```{r sum_csf, echo=FALSE}
summary(data_csf) 
```

### ANR data

```{r sum_anr, echo=FALSE}
summary(data_anr) 
```

## CSF Dataset preview

```{r head_csf, echo=FALSE, message=FALSE, warning=FALSE}

data_csf %>%
    slice_head(n =5) %>% 
    mutate(across(where(is.character), ~stringr::str_replace(.x,
                                                      "(^.{20}).*",
                                                      "\\1 \\.\\.\\."
                                                      ))) %>% 
    knitr::kable() 

```

### Variables - description

-   `project_code` unique identifier of a project

-   `title_cz` title of the project in Czech

-   `title_eng` title of the project in English

-   `provider` Identifier of the funding provider

    -   **GA0** Czech Science Foundation

-   `program_code` identifier of the competition program

    -   **GA** Standard projects. 1993-ongoing

    -   **GE** Eurocores

    -   **GP** Postdoctoral projects. 1998-ongoing

    -   **GC** International projects. 2007-ongoing

    -   **GD** Doctoral projects. 2003-ongoing

    -   **GB** Excellence support projects. 2012-2018

    -   **GF** LEAD Agency international projects. 2015-ongoing

    -   **GJ** Junior projects. **2015-ongoing**

    -   **GX** Excellence projects. 2019-ongoimng

-   `program_title` name of the competition program (in Czech)

-   `disc_group` field of research according to original Czech
    classification system (until 2017)

-   `disc` primary research discipline according to original Czech
    classification system (until 2017)

-   `disc_secondary` secondary research discipline according to original
    Czech classification system (until 2017), if multidisciplinary

-   `disc_tertiary` tertiary research discipline according to original
    Czech classification system (until 2017), if multidisciplinary

-   `ford` field of research according to FORD (after 2017)

-   `ford_secondary` field of research according to FORD (after 2017),
    if multidisciplinary

-   `ford_tertiary` field of research according to FORD (after 2017), if
    multidisciplinary

-   `year_start` first year of the project

-   `year_end` final year of the project

-   `research_category` classification of the type of research

    -   **ZV** basic (fundamental) research

-   `evaluation` evaluation of completed projects

    -   **V** excellent

    -   **U** - successful

    -   **O** -unsuccessful, no contract breach

    -   **S** - unsuccessful, contract breach

    -   **NA** - missing

-   `total` total amount of funding

-   `national_public` amount of funding from national public resources

-   `foreign_public` amount of funding from foreign resources

-   `private_total` amount of funding from the private sector

-   `other_public` amount of funding from other public resources

-   `abstract` description of the project goals

-   `keywords` keywords of the project

## ANR Dataset preview

```{r head_anr, echo=FALSE, message=FALSE, warning=FALSE}

data_anr %>%
    slice_head(n =5) %>% 
    mutate(across(where(is.character), ~stringr::str_replace(.x,
                                                      "(^.{20}).*",
                                                      "\\1 \\.\\.\\."
                                                      ))) %>% 
    knitr::kable() 

```

### Variables - description

-   `code_du_projet` [text] Code du projet

-   `titre` [text] Titre

-   `acronyme` [text] Acronyme

-   `resume` [text] Résumé

-   `annee_de_financement` [text] Année de financement

-   `lien_projet` [text] Lien Projet

-   `code_du_programme` [text] Code du programme

-   `programme` [text] Programme

-   `lien_programme` [text] Lien Programme

-   `perspectives` [text] Perspectives

-   `publications_et_brevets` [text] Publications et brevets

-   `resultats` [text] Résultats

-   `resume_de_la_soumission` [text] Résumé de la soumission

-   `montant` [double] Montant

-   `date_de_debut` [date] Date de début

-   `duree_en_mois` [int] Durée en mois

-   `coordinateur_du_projet` [text] Coordinateur du projet

-   `identifiant_de_partenaire` [text] Identifiant de partenaire

-   `type_d_identifiant` [text] Type d'identifiant

-   `libelle_de_partenaire` [text] Libellé de partenaire

-   `sigle_de_partenaire` [text] Sigle de partenaire

-   `code_du_type_de_partenaire` [text] Code du type de partenaire

-   `type_de_partenaire` [text] Type de partenaire
