---
title: "External data sources"
format: html
---

This sub-project is intended for the acquisition and processing of external data that are to be used as raw data in the default `targets` project.

## Setup

### Targets environment for subproject

```{r}
#| label: define_project
#| include: false
Sys.setenv(TAR_PROJECT = "data_raw")
```

### Targets script setup

```{r}
#| label: setup
#| include: false
library(targets)
tar_unscript(script = "_data_raw.R")
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```


### Targets globals

We first define some global options/functions common to all targets.

```{r}
#| engine: targets
#| label: globals
#| tar_globals: true

# read custom functions
lapply(list.files(here::here("R"), full.names = TRUE), source)
tar_option_set(packages = packages())
```

### Pinboard setup

Path to where the pin board should be located on the local machine. This should be a folder on a connected ownCloud folder.
```{r}
#| engine: targets
#| label: board_path
#| tar_globals: true


# PINS_BOARD var is defined in usethis::edit_r_environ("project")
path_to_pin_board <- Sys.getenv("PINS_BOARD")
```

Register the pin board.

```{r}
#| engine: targets
#| label: pin_board
list(
  tar_target(
    name = topfun_board,
    command = pins::board_folder(path_to_pin_board, versioned = FALSE)
  )
)
```

## PINS

```{r}
#| engine: targets
#| label: pins
list(
  tar_target(
    name = csf_pin,
    command = pin_data(board = topfun_board,
                       src = "https://owncloud.cesnet.cz/index.php/s/HIm7FEYQIMfoBuu/download",
                       src_format = "tsv",
                       name = "data_csf_df_file",
                       title = "Czech Science Foundation Dataset",
                 description = "A dataset of CSF funded projects obtained from the CEP database.",
                 metadata = list("license" = "Public domain")
                       ),
    format = "feather"
  ),
  tar_target(
  name = anr_pin,
    command = pin_data(board = topfun_board,
                       src = "https://static.data.gouv.fr/resources/anr-01-projets-anr-dos-detail-des-projets-et-des-partenaires/20230705-101003/anr-dos-depuis-2010-projets-finances-20230705-projets.csv",
                       src_format = "csv_fr",
                       name = "data_anr_df_file", 
                 title = "Agence nationale de la recherche Dataset",
                 description = "A dataset of ANR funded projects obtained from https://www.data.gouv.fr/fr/datasets/r/87d29a24-392e-4a29-a009-83eddcff3e66.",
                 metadata = list("license" = "Ouvert"), versioned = FALSE
                       ),
    format = "feather"
  ),
tar_target(
  name = erc_pin,
    command = pin_data(board = topfun_board,
                       src = "https://owncloud.cesnet.cz/index.php/s/wYTYM2o5Tj1xr8j/download",
                       src_format = "csv2",
                       name = "data_erc_df_file", 
                 title = "European Research Council Dataset",
                 description = "A dataset of ERC funded projects obtained from CORDIS database",
                 metadata = list("license" = "European Commission reuse notice"), versioned = FALSE
                       ),
    format = "feather"
  )

  
)
```


## Manifest
```{r}
#| engine: targets
#| label: update_manifest_pins
list(
  tar_target(
    name = manifest_pins,
    command = pins::write_board_manifest(topfun_board)
    )
)
```