---
title: "External data sources"
format: html
---

This sub-project is intended for the acquisition and processing of external data that are to be used as raw data in the default `targets` project.

## Setup

### Targets environment for project

```{r}
#| label: define_project
#| include: false
Sys.setenv(TAR_PROJECT = "external")
```

### Run project specific pipeline

```{r}
#| label: run_pipeline
#| eval: false
start <- Sys.time()
targets::tar_make(script = "_external.R", store = "_external")
Sys.time()-start
```

### Targets script setup

```{r}
#| label: setup
#| include: false
library(targets)
tar_unscript(script = "_external.R")
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```


### Targets globals

We first define some global options/functions common to all targets.

```{r}
#| engine: targets
#| label: globals
#| tar_globals: true

# read custom functions
lapply(list.files(here::here("R"), full.names = TRUE), source)
tar_option_set(packages = packages())
```

### Pinboard setup

Path to where the pin board should be located on the local machine. This should be a folder on a connected ownCloud folder.
```{r}
#| engine: targets
#| label: board_path
#| tar_globals: true


# PINS_BOARD var is defined in usethis::edit_r_environ("project")
path_to_pin_board <- Sys.getenv("PINS_BOARD")
```

Register the pin board.

```{r}
#| engine: targets
#| label: pin_board
list(
  tar_target(
    name = topfun_board,
    command = pins::board_folder(path_to_pin_board, versioned = FALSE)
  )
)
```

## HAL

```{r}
#| engine: targets
#| label: hal
list(
  tar_target(
    name = hal_types,
    command = c("ART", "COUV", "COMM", "OUV")
  ),
  tar_target(
    name = hal_years,
    command = seq(2008, 2012, 1)
  ),
  tar_target(
    name = hal,
    command = call_hal(hal_types, hal_years, run = as.logical(Sys.getenv("API_RUN"))),
    pattern = cross(hal_types, hal_years)

  )
)
```
