---
title: "Master of projects"
format:
  html:
    code-fold: true
---

## HAL API

This is obsolete code for quering HAL API. There is no need to run this subproject anymore.

- __Run__: No.
- __Requirement__: 
  - `API_RUN=TRUE` to be set in `.Renviron` file.

```{r}
#| label: data_import
#| eval: false
start <- Sys.time()
quarto::quarto_render("_external.qmd", quiet = TRUE)
targets::tar_make(script = "_external.R", store = "_external")
Sys.time()-start
```

## Raw data

This code needs to be run only if data sources change and need to be updated. You should only compile this subproject if you know what you are doing and why you are doing it.

- __Run__: Not required.
- __Requirement__: 
  - `PINS_BOARD=PATH_TO_PINBOARD` to be set in `.Renviron` file


```{r}
#| label: data_import
#| eval: false
quarto::quarto_render("_data_raw.qmd", quiet = TRUE)
targets::tar_make(script = "_data_raw.R", store = "_data_raw")
```

## Pinboard

This code needs to be run only if data sources change and need to be updated. In principle, this is not required except when initializing the project. 

- __Run__: When initializing the analytical project or when checking for updated data inputs.
- __Requirement__:
  - `MANIFEST_URL=URL/_pins.yaml` to be set in `.Renviron` file. 
  - internet connection.

```{r}
#| label: data_import
#| eval: false
quarto::quarto_render("_pinboard.qmd", quiet = TRUE)
targets::tar_make(script = "_pinboard.R", store = "_pinboard")
```

## Run main pipeline

This is the default pipeline. It serves for analysis of the raw data stored in the pinboard. 

- __Run__: Every time analysis is updated.
- __Requirement__: 
  - Pinboard source needs to be established by compiling the pinboard subproject at least once. 
  - Topic model subproject must be compiled.

```{r}
#| label: default_project
#| eval: false
quarto::quarto_render("_targets.qmd", quiet = TRUE)
targets::tar_make(script = "_targets.R", store = "_targets")
```