---
title: "Overview of the data on French, Czech, and EU science funding agencies"
format:
  html:
    toc: true
execute:
  echo: false
params:
  targets_store: "../_targets"
---

```{r setup}
#| include: false
library(targets)
library(tidyverse, quietly = TRUE)
```

```{r setup_store}
#| eval: false
#| include: false
params$targets_store <- "_targets"
```

## Combined dataset

```{r combined_dataset}
tar_load(data_all, store = params$targets_store)
```

Number of combined observations: `r nrow(data_all)`

Variables: `r colnames(data_all)`

### Data by countries and type of competition

Split by country.
```{r}
data_all %>% count(country) %>% 
    kableExtra::kable(format = "markdown")
```

Split by country and type of competition.
```{r}
data_all %>% count(country, type) %>% 
    kableExtra::kable(format = "markdown")
```

Number of projects in each year by country and competition type.
```{r}
tar_read(data_all_type_plot, store = params$targets_store)
```

Amount of funding awarded in each year by country and competition type. For the Czech case, 1 EUR = 25 CZK conversion was used.
```{r}
tar_read(data_all_funding_plot, store = params$targets_store)
```

Mean amount of funding per project awarded in each year by country and competition type.
```{r}
tar_read(data_all_mean_plot, store = params$targets_store)
```

Mean amount of funding per one year of project duration awarded in each year by country and competition type.
```{r}
tar_read(data_all_mean_yearlyplot, store = params$targets_store)
```

## Topic models

Top 5 words per topic.

::: {.panel-tabset}
### CSF topics.

```{r csf_topic_plot}
#| fig.height: 12
#| fig.width: 9
tar_read(topics_csf_plot_level_1, store = params$targets_store) +
    facet_wrap(~topic, ncol = 6, scales = "free") +
    theme(axis.text.x = element_blank(),
          axis.title = element_blank())
```

### ERC topics.

```{r erc_topic_plot}
#| fig.height: 12
#| fig.width: 9
tar_read(topics_erc_plot_level_1, store = params$targets_store) +
    facet_wrap(~topic, ncol = 6, scales = "free") +
    theme(axis.text.x = element_blank(),
          axis.title = element_blank())
```

### ANR topics.

```{r anr_topic_plot}
#| fig.height: 12
#| fig.width: 9
tar_read(topics_anr_plot_level_1, store = params$targets_store) +
    facet_wrap(~topic, ncol = 6, scales = "free") +
    theme(axis.text.x = element_blank(),
          axis.title = element_blank(),
          axis.ticks.x = element_blank())
```
:::

## Topic distributions

The following graphs show histograms of topic values across documents. Heavy-tailed topics tend to be distinctive, whereas near-normally distributed topics tend to be uniformative.

::: {.panel-tabset}
### CSF topics.

```{r csf_topic_distr_plot}
#| fig.height: 12
#| fig.width: 9
tar_read(topic_distribution_plots, store = params$targets_store)[[3]] +
    facet_wrap(~topic, scales = "free", ncol = 6)
```

### ERC topics.

```{r erc_topic_distr_plot}
#| fig.height: 12
#| fig.width: 9
tar_read(topic_distribution_plots, store = params$targets_store)[[2]] +
    facet_wrap(~topic, scales = "free", ncol = 6)
```

### ANR topics.

```{r anr_topic_distr_plot}
#| fig.height: 12
#| fig.width: 9
tar_read(topic_distribution_plots, store = params$targets_store)[[1]] +
    facet_wrap(~topic, scales = "free", ncol = 6)
```
:::